\chapter{Introduction}

\textbf{ACT 1, SCENE 1}\par

[White text appears, letter by letter, in the middle of the screen. As it appears, it also makes a soft and comfy typing sound.] \par

\vspace{1cm}PROLOGUE: \par

All starts with an infinite black background, with no history, with nothing else but an empty sea of possibilities...  But as the infinite fills the emptiness, the idea, the white letters in front of the monitor, began to kill that 2D plane. All of that, to make it converge into a beauty, beauty created history by no one. \par

Into that emptiness now is a squared screen, delimited by it's own size and inside, a simple creation that records all into an ordinary book, in an ordinary world, with his ordinary freedom. \par

Now that I, the creator, killed the identity of infinity and created the creation; is time to me to disappear and let it be. Let it play. Let him by his own and his fully freedom. \par

\vspace{3cm}

\textbf{ACT 1, SCENE 2}\par
[The typing sound changes to another more light and less ominous. Also the background starts to blink slowly and softly.]

\vspace{1cm}SHLY\par
(Moaning while the text begins to slide on the top of the screen.) \par
Whoa! What did happen? \par

\vspace{0.5cm}
(speaking to himself) \par
Such a dream... Is like now, after 22 years of being lost and not knowing what to do with my life, suddenly, I understand the purpose of the existence itself. And my mission!\par

\vspace{0.5cm}
[The scenario lights up and reveals the bedroom of SHLY and all his bedroom miscellaneous.]
\vspace{0.5cm}

SHLY\par
(Excited and yelling)\par
I will record all I see, all I do, all I feel; inside of this random book I have! (Laughs maniacally)\par

\vspace{1cm}

MOM\par
(Far away yelling too)\par
Honey, prepare yourself and come down to breakfast. You are gonna be late.

\vspace{1cm}

SHLY\par
Ok mom! I'll go down soon. \par

\vspace{0.5cm}
(Speaking to himself)\par
Ok, I'll grab the notebook, a pen and a book to record while having breakfast...

\vspace{0.5cm}
[Complete freedom to choose the book before going down]
\begin{itemize}
    \item History book. $\rightarrow$ Read act 1, scene 3, \textit{history} \ref{act1: History}
    \item Philosophy book. $\rightarrow$ Read act 1, scene 3, \textit{philosophy} \ref{act1: Philosophy}
    \item Empty notebook. $\rightarrow$ Read act 1, scene 3, \textit{Empty} \ref{act1: Empty}
\end{itemize}
\vspace{0.5cm}

\vspace{3cm}

\section*{}
\textbf{ACT 1, SCENE 3, HISTORY}\label{act1: History}\par 
[After grabbing the book and going downstairs, SHLY sits on a chair in front of the table and starts eating.]

SHLY\par
(While eating)\par
¡Mhmm...! Such a tasty breakfast mom!\par

\vspace{1cm}

MOM\par
Thank you honey, always to thank that you appreciate the breakfast. But you don't have to say it all the mornings.

\vspace{1cm}

SHLY\par
I know, but is the truth.

\vspace{1cm}

MOM\par
Never mind.

\vspace{1cm}

SHLY\par
(While eating starts reading the first chapter of the history book.)\par



\vspace{3cm}

\section*{}
\textbf{ACT 1, SCENE 3, PHILOSOPHY}\label{act1: Philosophy}\par

\vspace{3cm}

\section*{}
\textbf{ACT 1, SCENE 3, EMPTY}\label{act1: Empty}\par